Sir Alex Ferguson's Continued Tenure Could Have Only Marginal Improvements over Manchester United's EPL Performance

### 2024-04-16 paper/paper.qmd
Added README.md and recompiled paper.qmd.

---
title: "Sir Alex Ferguson's Continued Tenure Could Have Only Marginal Improvements over Manchester United's EPL Performance"
subtitle: "An Analysis of an Increase in League Points"
author: 
  - Aryaman Sharma
thanks: "Code and data are available at: https://github.com/Ary4m3n/manchester-united.git"
date: today
date-format: long
abstract: "Manchester United has been a historical football club. This paper examines Manchester United's performance from 2004-2013 under Sir Alex Ferguson's golden era and compares it with the period from 2014-2023, following his retirement. Using a Bayesian analysis model, this paper attempts to predict potential league points for if Sir Alex would have continued managing (2014-2023). Results predict only a marginal improvement in club's performance. This reasearch delves into recent increase in competition and other factor as a possible explanation."
format: 
  pdf:
    tbl-pos: "h"
    fig-pos: "h"
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Sir Alex Ferguson's Continued Tenure Could Have Only Marginal Improvements over Manchester United's EPL Performance"
author: 
  - Aryaman Sharma
thanks: "Code and data are available at: https://github.com/Ary4m3n/manchester-united.git"
date: today
date-format: long
abstract: "Manchester United has been a historical football club. This paper examines Manchester United's performance from 2004-2013 under Sir Alex Ferguson's golden era and compares it with the period from 2014-2023, following his retirement. Using a Bayesian analysis model, this paper attempts to predict potential league points for if Sir Alex would have continued managing (2014-2023). Results predict only a marginal improvement in club's performance. This reasearch delves into recent increase in competition and other factor as a possible explanation."
format: 
  pdf:
    tbl-pos: "h"
    fig-pos: "h"
toc: true
number-sections: true
bibliography: references.bib
---
